### 2018-10-29 write-up/paper/intro.tex
Add frac. perm. sub. lemma

\lang\ allows a novice to understand and work with complicated linear algebra
library APIs, as well as point out subtle aliasing bugs and reduce memory usage
in existing programs. In fact, we were able to use \lang\ to find linearity and
aliasing bugs in a linear algebra program that was \emph{generated} by another
program \emph{specifically designed to translate matrix expressions into an
efficient sequence of calls linear algebra routines}. We were also able to
reduce the number of temporaries used by the same program, using \lang's type
system to guide us.

>>>>

\lang\ allows a novice to understand and work with complicated linear algebra
library APIs, as well as point out subtle aliasing bugs and reduce memory usage
in existing programs. In fact, we were able to use \lang\ to find linearity and
aliasing bugs in a linear algebra program that was \emph{generated} by another
program \emph{specifically designed to translate matrix expressions into an
efficient sequence of calls to linear algebra routines}. We were also able to
reduce the number of temporaries used by the same program, using \lang's type
system to guide us.

### 2018-10-29 write-up/semantics/lemmas.tex
Add points about finding bugs
Finish desugaring and matrix expression figures
Add frac. perm. sub. lemma

$\theta$ is irrelevant because it only maps fractional capability variables to
fractional capabilities. By construction, $\delta$ and $\gamma$ only map
variables to values, and values are closed under substitution.

@@

@@

\subsection{$\forall \Delta, \Gamma, t, k, \theta, \delta, \gamma.\ %
    \delta \in \den{I}{k}{\Delta}\theta \wedge \gamma \in \pi_2[\den{L}{k}{\Gamma}\theta]
    \Rightarrow \dom(\Delta) = \dom(\delta)$ and $\dom(\Gamma) = \dom(\gamma)$}\label{samedom}

@@

>>>>

$\theta$ is irrelevant because it only maps fractional permission variables to
fractional permissions. By construction, $\delta$ and $\gamma$ only map
variables to values, and values are closed under substitution.

@@

(Here, $\theta$ is the empty substitution for $\varsigma = \den{H}{}{\sigma}\theta$.)

@@

\subsection{$\forall \Delta, \Gamma, t, k, \theta, \delta, \gamma.\ %
    \delta \in \den{I}{k}{\Delta}\theta \wedge \gamma \in \pi_2[\den{L}{k}{\Gamma}\theta]
    \Rightarrow \\ \dom(\Delta) = \dom(\delta)$ and $\dom(\Gamma) = \dom(\gamma)$}\label{samedom}

@@

\subsection{$\forall e, \sigma, e', \sigma', \theta.\
    \langle e, \sigma \rangle \rightarrow \langle e' , \sigma' \rangle
    \Rightarrow \langle \theta(e), \theta(\sigma)
    \rangle \rightarrow \langle \theta(e') , \theta(\sigma') \rangle$}

\pf~By induction on $\rightarrow$.
\begin{proof}

    \step{}{\assume{Arbitrary $e, \sigma, e', \sigma', \theta$ such that 
        $\langle e, \sigma \rangle \rightarrow \langle e' , \sigma' \rangle$.}}

    \step{}{\suffices{To consider only the following rules which mention
        fractional permission variables.}
        \textsc{Op\_Frac\_Perm}, \textsc{Op\_Share}, \textsc{Op\_Unshare\_(N)Eq}
        and \textsc{Op\_Gemm\_(Mis)Match}.}

    \step{}{\case{\textsc{Op\_Frac\_Perm.}}{Because substitution avoids capture,
        \\ $\langle \theta((\ottkw{fun} fc \rightarrow v) \, [f]),
        \theta(\sigma) \rangle \rightarrow \langle \theta(v\, [fc/f]),
        \theta(\sigma'\, [fc/f]) \rangle$.}}

    \step{}{The rest of the cases are parametric in their use of fractional
        permission variables and so will take the same step ater any substitution.}

    \step{}{\textsc{Corollary:}
        If $\langle e\, [fc/f_1], \sigma \, [fc/f_1] \rangle \rightarrow^n
        \langle v_2, \sigma_2 \rangle$ and
        $\langle e\, [fc/f_2], \sigma \, [fc/f_2] \rangle \rightarrow^n
        \langle v_2, \sigma_2 \rangle$, then
        $\exists\,v, \sigma.\ v_1 = v\,[fc/f_1] \wedge v_2 = v\,[fc/f_2]
        \sigma_1 = \sigma\,[fc/f_1] \wedge \sigma_2 = \sigma\,[fc/f_2]$.}
